Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-08-06 talk/vmil2012/paper.tex
Rewrite paragraph about guard frequency

Figure~\ref{fig:benchmarks} shows the total number of operations that are
recorded during tracing for each of the benchmarks and what percentage of these
are guards. Figure~\ref{fig:benchmarks} also shows the number of operations
left after performing the different trace optimizations done by the trace
optimizer, such as xxx. The last columns show the overall optimization rate and
the optimization rate specific for guard operations, showing what percentage of
the operations were removed during the optimizations phase.
Figure~\ref{fig:benchmarks} shows that as can also be seen on
Figure~\ref{fig:guard_percent} the optimization rate for guards is on par with
the average optimization rate for all operations in a trace. After optimization
the amount of guards left in the trace still represents about 15.18\% to
20.22\% of the operation, a bit less than before the optimization where guards
represented between 15.85\% and 22.48\% of the operations. After performing the
optimizations the most common operations are those that are difficult or
impossible to optimize, such as JIT internal operations and different types of
calls. These account for 14.53\% to 18.84\% of the operations before and for
28.69\% to 46.60\% of the operations after optimization. These numbers show
that about one fifth of the operations, making guards one of the most common
operations, that are compiled are guards and have associated with them the
high- and low-level datastructes that are reconstruct the state.

>>>>

\todo{a description about what each selected benchmark does}

From the mentioned benchmarks we collected different datasets to evaluate the
Frequency, the overhead and overall behaviour of guards.
Figure~\ref{fig:benchmarks} summarizes the total number of operations that were
recorded during tracing for each of the benchmarks and what percentage of these
operations are guards. The number of operations was counted on the unoptimized
and optimized traces. Showing that the overall optimization rate is between
65.80\% and 86.23\% of all operations and that the optimization rate for guards
is similar to the general one, as could be assumed based on
Figure~\ref{fig:guard_percent}. These numbers show that guards are a rather
common operation in the traces, which is a reason the put effort into
optimizing them.
\todo{some pie charts about operation distribution}
